Simulating dynein's powerstroke using Brownian dynamics

### 2017-05-11 thesis/latex/thesis.tex
Thesis: Mess around with latex header / .cls to make things look better.

\documentclass[
12pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

\usepackage{palatino} % Use the Palatino font by default

\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

@@

% Elliott-added packages
\usepackage{amsmath}
\usepackage{listings}
\usepackage{float}

@@

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=2.5cm, % Inner margin
	outer=2.5cm, % Outer margin
	bindingoffset=.5cm, % Binding offset
	top=1.5cm, % Top margin
	bottom=1.5cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}

@@

\subject{Physics} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://www.university.com}{Oregon State University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{http://physics.oregonstate.edu}{Physics}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{http://physics.oregonstate.edu/~roundyd/}{Roundy Research Group}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
Dynein is a motor protein which transports cargo along tracks inside the cell. Like related motor proteins kinesin and myosin, dynein uses cellular energy to take steps with its two foot domains. Unlike kinesin or myosin, dynein's stepping pattern is highly varied: it can take steps between zero and 60nm in both the forwards and backwards directions. It is believed that dynein takes such broad, stochastic steps because its large size and several elastic regions make it more influenced by Brownian motion. To test this, we model the motor as a 2D system of elastic hinges, then simulate this model using Brownian dynamics. Preliminary results indicate such a model is capable of taking steps between zero and 25nm. These results give hope that, with further tweaking, the model may be able to generate both larger steps and backwards steps.
\end{abstract}

@@

\tableofcontents % Prints the main table of contents

\listoffigures % Prints the list of figures

\listoftables % Prints the list of tables

%----------------------------------------------------------------------------------------
%	ABBREVIATIONS
%----------------------------------------------------------------------------------------

\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)

\textbf{MT} & \textbf{M}icro\textbf{t}ubule\\
\textbf{MTBD} & \textbf{M}icro\textbf{t}ubule \textbf{B}inding \textbf{D}omain\\

\end{abbreviations}

@@

\chapter{Theory}
\label{chap:Theory}

@@

\chapter{Methods}
\label{chap:Methods}
This section will go into detail on how the model was implemented in code, verified for accuracy, and how its parameters were fit to experiment.\\

@@

\chapter{Results \& Discussion}
\label{chap:ResultsAndDiscussion}

@@

\chapter{Conclusion}
\label{chap:Conclusion}

>>>>

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

\usepackage{lmodern} % Use the Palatino font by default

\usepackage[backend=bibtex,style=numeric,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

@@

% Elliott-added packages
\usepackage{amsmath} % for align and other environments
\usepackage{listings}
\usepackage{float}   % for H figure specifier
\usepackage{indentfirst} % to indent after sections

@@

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=2.5cm, % Inner margin
	outer=2.5cm, % Outer margin
	bindingoffset=.0cm, % Binding offset
	top=1.5cm, % Top margin
	bottom=1.5cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}

@@

\subject{Physics} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://www.university.com}{Oregon State University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{http://physics.oregonstate.edu}{Oregon State University Department of Physics}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{http://physics.oregonstate.edu/~roundyd/}{Roundy Research Group}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
Dynein is a motor protein which transports cargo along tracks inside the cell. Like related motor proteins kinesin and myosin, dynein uses cellular energy to take steps with its two foot domains. Unlike kinesin or myosin, dynein's stepping pattern is highly varied: it can take steps between zero and 60nm in both the forwards and backwards directions. It is believed that dynein takes such broad, stochastic steps because its large size and several elastic regions make it more influenced by Brownian motion. To test this, we model the motor as a 2D system of elastic hinges, then simulate this model using Brownian dynamics. Preliminary results indicate such a model is capable of taking steps between zero and 25nm. These results give hope that, with further tweaking, the model may be able to generate both larger steps and backwards steps.
\end{abstract}
\newpage

@@

\tableofcontents % Prints the main table of contents
\newpage

\listoffigures % Prints the list of figures
\newpage

\listoftables % Prints the list of tables
\newpage

%% %----------------------------------------------------------------------------------------
%% %	ABBREVIATIONS
%% %----------------------------------------------------------------------------------------

%% \begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)

%% \textbf{MT} & \textbf{M}icro\textbf{t}ubule\\
%% \textbf{MTBD} & \textbf{M}icro\textbf{t}ubule \textbf{B}inding \textbf{D}omain\\

%% \end{abbreviations}

@@

\newpage
\chapter{Theory}
\label{chap:Theory}

@@

\newpage
\chapter{Methods}
\label{chap:Methods}
This section will go into detail on how the model was implemented in code, verified for accuracy, and how its parameters were fit to experiment.\\

@@

\newpage
\chapter{Results \& Discussion}
\label{chap:ResultsAndDiscussion}

@@

\newpage
\chapter{Conclusion}
\label{chap:Conclusion}
